Comparison of canopy height measurement between TLS and Sentinel2 data

### 2023-07-27 submission_4/submission_4.qmd
Finishes missing sentence
smaller AOI

This section lists, describes and tries to explain the plots and graphs generated by the algorithm described in the previous section.

@@

The TLS height measurement is shown in @fig-tls-heights. It can be seen in the left plot that the TLS data is potentially far more fine grained than the data of the Senitnel2 satellite (see @fig-sentinel-height). 
For proper comparison the TLS got resampled to match the resolution of the sentiel data (see @fig-tls-heights)
The difference in granularity can also been seen in the comparison of distribution of height and the standard derivations (see @fig-comparison-histograms): 
While the height of TLS data is distributed evenly about the the whole height spectrum, the sentinel 2 data maps the whole area to a span of around 30 meters. 
This can also be seen in @fig-sentinel-height, which uses the same colormap as @fig-tls-heights, but is very uniformly distributed.

@@

We computed the residuals by using the far more fine grained TLS data as truth and subtract the sentiel data from it. The result can be see in @fig-residuals-stats. 
But there are a few things to consider:
1. As briefly explained in the prevoius section, lower branches can occlude the actual canopy, resulting in an underestiation of the canopy height
2. Also the further away from the device a tree is, the more likely it is to be (partly) occluded by closer objects.

As expected, the Sentinel 2 data generally overestimates the canopy height, with a far larger part having negative residuals (colored red in @fig-residuals-stats). 
Interestingly a small section in the map (bottom right, the area with the highest trees according to TLS data)

@@

In conclusion, it is shown that TLS and satellite data differ greatly in terms of granularity and variance, which is to no surprise. 
Of course, the big advantage of using satellites, covering waste amout of area, is looked over in this approach to make it compareable to the TLS by selecting only such a small area.
Furthermore, it is not entirely clear how good the values from the TLS actually are. 
We used it as ground truth for calculating the residuals from the Sentinel data, but there are actually a few problems with this method, as explained before. 
An interesting approach would be comparing TLS data to UAV data, which could show the possible underestimation of the TLS.

So all in all, satellites are well suited for measuring vast areas, but lack the necessary precision to be used in pprecise, local measurements.
On the other hand, TLS also has some systematic problems, which may be overcome by certain methods (multiple scanning from different locations and merge of the results, scanning at a higher level etc.).

>>>>

This section lists, describes and explains the plots and graphs generated by the algorithm described in the previous section.

@@

The TLS height measurement is shown in @fig-tls-heights. It can be seen in the left plot that the TLS data is far more fine grained than the data of the Senitnel2 satellite (see @fig-sentinel-height). 
For better comparison the TLS got resampled to match the resolution of the sentiel data (see @fig-tls-heights)
The difference in granularity can also been seen in the comparison of distribution of height and the standard derivations (see @fig-comparison-histograms): 
While the height of TLS data is distributed evenly across the the whole height spectrum, the sentinel 2 data maps the whole area to around 30 meters. 
This can also be seen in @fig-sentinel-height, which uses the same colormap as @fig-tls-heights, but is very uniformly distributed.

@@

We computed the residuals by using the far more finely resolved TLS data as truth and subtract the sentiel data from it. The result can be seen in @fig-residuals-stats. 
But there are a few things to consider:
1. As briefly explained in the prevoius section, lower branches can occlude the actual canopy, resulting in an underestiation of the canopy height
2. Also the further away from the device a tree is, the more likely it is to be (partly) occluded by closer objects.

As expected, the Sentinel 2 data generally overestimates the canopy height, with a far larger part having negative residuals (colored red in @fig-residuals-stats). 
Interestingly only a small section in the map (bottom right, the area with the highest trees according to TLS data) is underestimated.

@@

In conclusion, it is shown that TLS and satellite data differ greatly in terms of resolution and variance, which is no surprise. 
Of course, the big advantage of using satellites, that can cover much larger areas, is over looked in this approach to make it compareable to the TLS by selecting only a small area.
Furthermore, it is not entirely clear how good the values from the TLS actually are. 
We used it as ground truth for calculating the residuals from the Sentinel data, but there are actually a few problems with this method, as explained before. 
An interesting approach would be comparing TLS data to UAV data, which could show the possible underestimation of the TLS.

So all in all, satellites are well suited for measuring vast areas, but lack the necessary precision to be used in precise, local measurements.
On the other hand, TLS also has some systematic problems, which may be overcome by certain methods (multiple scanning from different locations and merge of the results, scanning at a higher level etc.).
